### 2022-12-01 abstract.tex
Lisa feedback

The first and largest part of this thesis consists of three extensions of a
recently proposed reverse-Bayes method for quantifying replication success. The
key idea of the method is to challenge the data from the original study with a
sceptical prior so that the resulting posterior no longer provides evidence for
the finding from the study. The first extension recalibrates the proposed method
to produce more appropriate inferences in terms of effect size.
% from the relative effect size perspective
The recalibration is chosen such that for original studies which were borderline
significant, replication success can only be achieved if the effect estimate
from the replication study is larger than the estimate from the original study.
The recalibrated method has good frequentist properties comparable to standard
methods used in practice. The second extension replaces tail probabilities with
Bayes factors as measures of evidence.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
We find that the extended method combines two notions of replicability: It
requires that original and replication study independently provide evidence for
an effect and ensures that their effect estimates are compatible. The extended
method also avoids a statistical paradox which the initial method suffered from.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third and last extension provides a framework for Bayesian design of
replication studies which allows for combining data from the original study with
external knowledge. External knowledge, such as data from other studies, is
ubiquitous in the replication setting and taking it into account can potentially
lead to more efficient designs compared to classical approaches.

The second part of the thesis is also concerned with reverse-Bayes methodology
but with a wider ranger of applications than only replication studies. The
reverse-Bayes idea was first proposed in the 1950s, but it has mostly been
forgotten. To increase awareness and show potential use cases, reverse-Bayes
history and methods are summarized in a comprehensive review. The review
includes also some new results on connections between revere-Bayes methods and
meta-analysis. Finally, a commentary paper on a recently proposed reverse-Bayes
method draws connections to other reverse-Bayes methods.

The last part of the thesis revolves around research integrity issues in
methodological research. Questionable research practices, such as selective
reporting of results, are often seen as main cause for the low replicability in
applied research. These practices can similarly harm methodological research,
but are often not recognized. To raise awareness, an illustrative simulation
study is conducted in which it is shown how a novel method can easily be
presented as superior over established competitor methods if questionable
research practices are employed.

>>>>

The first and largest part of this thesis consists of three extensions to a
recently proposed reverse-Bayes method for quantifying replication success. The
key idea of the method is to challenge the data from the original study with a
sceptical prior so that the resulting posterior no longer provides evidence for
the finding from the study. Replication success is then achieved if there is
conflict between the sceptical prior and the replication data. The first
extension recalibrates the method to produce more appropriate inferences in
terms of effect size. The recalibration is chosen such that for original studies
which were borderline significant, replication success can only be achieved if
the effect estimate from the replication study is larger than the estimate from
the original study. The recalibrated method has good frequentist properties
comparable to standard methods used in practice. The second extension replaces
tail probabilities with Bayes factors as measures of evidence.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
% We find that the extended method combines two notions of replicability: It
% requires that original and replication study independently provide evidence for
% an effect and ensures that their effect estimates are compatible.
The extended method has similar properties as the initial method but avoids a
statistical paradox which the initial method suffers from -- in some situations
it may flag success replication success even though the effect estimate from the
replication is arbitrarily smaller than to the original one.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. External knowledge, such as data from other studies, is ubiquitous in
the replication setting and taking it into account can lead to potentially more
efficient designs compared to classical approaches.

The second part of the thesis also deals with reverse-Bayes methods, but with a
broader scope of applications than replication studies. The reverse-Bayes idea
was first proposed in the 1950s, but it has mostly been forgotten. To increase
awareness and show potential use cases, reverse-Bayes history and methods are
summarized in a comprehensive review. The review includes also some new results
on connections between revere-Bayes methods and meta-analysis. %  Finally, a
% commentary paper on a recently proposed reverse-Bayes method draws connections
% to other reverse-Bayes methods.

The last part of the thesis revolves around research integrity issues in
methodological research. Questionable research practices, such as selective
reporting of results, are often seen as main cause for replicability issues in
the medical and social sciences. These practices can similarly harm
methodological research, but are often not recognized. To raise awareness, an
illustrative simulation study is conducted in which it is shown how a novel
method can easily be presented as superior over established competitor methods
if questionable research practices are employed.
